---
title: Pacific giant salamander size and channel location in old growth and clear
  cut forest sections of Mack Creek, Oregon
author: "Madeline Oliver and Lizzy Schattle"
date: "11/23/2019"
output: html_document
---


```{r setup, echo = FALSE, message = FALSE, warning = FALSE, cache = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = FALSE)
```


## Introduction

## Data and Methods

## Results
***


```{r}
# -------------------------------------------
# Attach packages
# -------------------------------------------

library(tidyverse)
library(janitor)
library(here)
library(RColorBrewer)
library(tidyr)
library(directlabels)
library(plotly)
library(effsize)
library(kableExtra)

# -------------------------------------------
# Read in Mack Creek Vertebrates data
# -------------------------------------------

vertebrates_raw <- read_csv("mack_creek_vertebrates.csv") 

# Create data frame with only the data we will need to use in our analysis, clean names, lubridate date column, add a count column grouped by year and section, add columns with de-coded section and classification names

vertebrates <- vertebrates_raw %>%
  clean_names() %>%
  filter(species == "DITE") %>%
  select(year, sitecode, section, reach, unittype, length1, weight, sampledate) %>%
  mutate(date = lubridate::mdy(sampledate)) %>%
  group_by(year, section) %>%
  add_tally() %>%
  ungroup() %>%
  mutate(Section = recode(section,
                           CC = "Clear Cut",
                           OG = "Old Growth"),
         classification = recode(unittype,
                                 C = "Cascade",
                                 I = "Riffle",
                                 IP = "Isolated Pools",
                                 P = "Pool",
                                 R = "Rapid",
                                 S = "Step",
                                 SC = "Side Channel"))
  
```

### Salamander counts in Mack Creek

#### Comparison of annual salamander abundance in old growth versus clear cut sections of Mack Creek

```{r}
# Create linegraph of salamander abundance over time in old growth and clear cut sections
ggplot(data = vertebrates,
       aes(x = year,
           y = n,
           group = Section,
           color = Section)) +
  geom_line(show.legend = FALSE) +
  xlim(1992, 2022) +
  geom_dl(aes(label = Section), 
          method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.8)) +
  labs(x = "Year",
       y = "Salamander Counts in Mack Creek",
       caption = "Figure 1. Salamander abundance in old growth and clear cut sections of Mack Creek are shown from 1993 to 2017.") +
  theme_classic()

```


#### Comparison of salamander abundance by channel classification in old growth and clear cut sections of Mack Creek


```{r}
# Filter out salamander observations where classification in Isolated Pools, then create count table of classification and section
salamander_counts <- vertebrates %>%
  filter(classification == c("Cascade", "Riffle", "Pool", "Rapid", "Step", "Side Channel")) %>%
  filter(year == 2017) %>%
  count(classification, Section) %>%
  pivot_wider(names_from = classification, values_from = n)


# Make a nice contingency table with janitor adorn
salamander_props <- salamander_counts %>% 
  janitor::adorn_percentages(denominator = "row") %>% 
  adorn_pct_formatting(digits = 0) %>% 
  adorn_ns(position = "front") %>%
  rename(Section = Section)

kable(salamander_props,
      caption = "Table 1. 2017 salamander counts by channel classification in old growth and clear cut sections of Mack Creek") %>% 
  kable_styling()
  
```

```{r}
# Use chi square test to determine the significance of the difference in where in the channel salamanders are located between the two sections

chi_counts <- salamander_counts %>% 
  select(-Section)

# Run chi-square:
channel_chi <- chisq.test(chi_counts)

channel_chi

```

According to our Chi-squared test for independence, there is not a significant effect of forest condition on where in the channel salamanders are found. 


### Salamander weights in Mack Creek

#### Salamander weights in clear cut versus old growth sections in 2017

```{r}
# We use an unpaired two sample t-test to compare salamander weights in clear cut vs. old growth sections in 2017
vertebrates_2017 <- vertebrates %>%
    filter(year == 2017)

CC_2017 <- vertebrates %>%
  filter(section == "CC")
  
OG_2017 <- vertebrates %>%
  filter(section == "OG")

summary_CC_2017 <- CC_2017 %>%
  summarize(
    mean_weight = mean(weight, na.rm = TRUE),
    sd_weight = sd(weight, na.rm = TRUE),
    salamander_number = n())

summary_OG_2017 <- OG_2017 %>%
  summarize(
    mean_weight = mean(weight, na.rm = TRUE),
    sd_weight = sd(weight, na.rm = TRUE),
    salamander_number = n())

weight_2017_ttest <- t.test(weight ~ Section, data = vertebrates_2017)
weight_2017_cohen <- cohen.d(weight ~ Section, data = vertebrates_2017)
weight_2017_ttest

```

In 2017, the mean salamander weight at the clear cut sites was `r round(summary_CC_2017$mean_weight, 2)`, and the mean salamander weight at the old growth sites was `r round(summary_OG_2017$mean_weight, 2)`. The mean lobster size between clear cut sites and old growth sites did not differ significantly (t(`r round(weight_2017_ttest$parameter, 2)`) = `r round(weight_2017_ttest$statistic, 2)`, p = (`r round(weight_2017_ttest$p.value, 4)`) with a small effect size of `r round(weight_2017_cohen$estimate, 2)`. 



#### Salamanders weight in pools, cascades and side-channels in 2017

```{r}
# We use a one-way ANOVA to compare the weights of salamanders in pools, cascades and side-channels of Mack Creek in 2017

# First we visualize the distribution of weights by classification using a histogram and a qq plot
ggplot(data = vertebrates_2017, 
       aes(x = weight)) +
  geom_histogram(aes(fill = classification),
                 alpha = 0.5,
                 show.legend = FALSE,
                 bins = 15) +
  facet_wrap(~classification, scales = "free")

ggplot(data = vertebrates_2017, 
       aes(sample = weight)) +
  geom_qq(aes(color = classification),
                 alpha = 0.5,
                 show.legend = FALSE) +
  facet_wrap(~classification, scales = "free")

# This data does not look normally distributed, however we have a very large sample size so we will still use an ANOVA test to compare means



```



## Summary

## References

