---
title: Pacific giant salamander size and channel location in old growth and clear
  cut forest sections of Mack Creek, Oregon
author: "Madeline Oliver and Lizzy Schattle"
date: "11/23/2019"
output: html_document
---


```{r setup, echo = FALSE, message = FALSE, warning = FALSE, cache = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = FALSE)
```


## Introduction

## Data and Methods

## Results
***


```{r}
# -------------------------------------------
# Attach packages
# -------------------------------------------

library(tidyverse)
library(janitor)
library(here)
library(RColorBrewer)
library(tidyr)
library(directlabels)
library(plotly)
library(effsize)
library(kableExtra)

# -------------------------------------------
# Read in Mack Creek Vertebrates data
# -------------------------------------------

vertebrates_raw <- read_csv("mack_creek_vertebrates.csv") 

vertebrates <- vertebrates_raw %>%
  clean_names() %>%
  filter(species == "DITE") %>%
  select(year, sitecode, section, reach, unittype, length1, length2, weight, sampledate) %>%
  mutate(date = lubridate::mdy(sampledate)) %>%
  group_by(year, section) %>%
  add_tally() %>%
  ungroup()
  

```

### Salamander counts in Mack Creek

#### Comparison of annual salamander abundance in old growth versus clear cut sections of Mack Creek

```{r}

ggplot(data = vertebrates,
       aes(x = date,
           y = n,
           group = section,
           color = section)) +
  geom_line(show.legend = FALSE) +
  labs(x = "Year",
       y = "Salamander Counts in Mack Creek",
       caption = "Figure 1. Salamander abundance in old growth and clear cut sections of Mack Creek are shown from 1993 to 2017.") +
  theme_classic()

```




#### Comparison of salamander abundance by channel classification in old growth and clear cut sections of Mack Creek



### Variation in channel location of salamanders between old growth and clear cut sections of Mack Creek


### Salamander weights in Mack Creek

####Comparison of salamander weights in clear cut versus old growth sections of Mack Creek in 2017


#### Comparison of weights of salamanders in pools, cascades and side-channels of Mack Creek in 2017


## Summary

## References

